ParaChiCSVO2

### 2024-05-24 index.qmd
Built site for gh-pages

|                          | T1w          | T2w          | pcASL                                                               | SWI                                               |
|------------|------------|------------|----------------------|---------------|
| Sequence                 | 3D FSPGR     | 3D CUBE      | Multi-shot 3D \\\\ fast spin-echo                                   | 3D spoiled GRE flow-compensated                   |
| Phase-encoding direction | Coronal      | Sagittal     | Axial                                                               | Axial                                             |
| TR (ms)                  | 7.74         | 2,300        | 4,680                                                               | 30.9                                              |
| TE (ms)                  | 2.97         | 66.29        | 10.55                                                               | 5.24                                              |
| Flip angle               | 12$^{\circ}$ | 90$^{\circ}$ | 111$^{\circ}$                                                       | 20$^{\circ}$                                      |
| FOV (cm)                 | 20           | 20           | 24                                                                  | 25                                                |
| Acquisition Matrix       | 512 x 512    | 256 x 256    | 128 x 128                                                           | 256 x 256                                         |
| In-plane resolution (mm) | 0.39 x 0.39  | 0.78 x 0.78  | 1.875 x 1.875                                                       | 0.977 x 0.977                                     |
| Slice thickness (mm)     | 1            | 1            | 4                                                                   | 2, reconstructed to 1 mm with zero filling (ZIP2) |
| Number of slices         | 126          | 106          | 50                                                                  | 92                                                |
| Additional parameters    | n/a          | n/a          | 1,450 ms label period; 2,025 ms pulse lable; 24 control-label pairs | n/a                                               |
| Scan duration            | 4 min 39 s   | 5 min 1 s    | 5 min 26 s                                                          | 5 min 29 s                                        |

>>>>

|                          | T1w          | T2w          | pcASL                                                               | SWI                                               |
|------------|------------|------------|----------------------|---------------|
| Sequence                 | 3D FSPGR     | 3D CUBE      | Multi-shot 3D fast spin-echo                                        | 3D spoiled GRE flow-compensated                   |
| Phase-encoding direction | Coronal      | Sagittal     | Axial                                                               | Axial                                             |
| TR (ms)                  | 7.74         | 2,300        | 4,680                                                               | 30.9                                              |
| TE (ms)                  | 2.97         | 66.29        | 10.55                                                               | 5.24                                              |
| Flip angle               | 12$^{\circ}$ | 90$^{\circ}$ | 111$^{\circ}$                                                       | 20$^{\circ}$                                      |
| FOV (cm)                 | 20           | 20           | 24                                                                  | 25                                                |
| Acquisition Matrix       | 512 x 512    | 256 x 256    | 128 x 128                                                           | 256 x 256                                         |
| In-plane resolution (mm) | 0.39 x 0.39  | 0.78 x 0.78  | 1.875 x 1.875                                                       | 0.977 x 0.977                                     |
| Slice thickness (mm)     | 1            | 1            | 4                                                                   | 2, reconstructed to 1 mm with zero filling (ZIP2) |
| Number of slices         | 126          | 106          | 50                                                                  | 92                                                |
| Additional parameters    | n/a          | n/a          | 1,450 ms label period; 2,025 ms pulse lable; 24 control-label pairs | n/a                                               |
| Scan duration            | 4 min 39 s   | 5 min 1 s    | 5 min 26 s                                                          | 5 min 29 s                                        |
